Automated topic naming to support analysis of software maintenance activities

### 2010-08-19 icse/icse2011.tex

\begin{document}
\numberofauthors{5}
\author{
\alignauthor 
Abram Hindle\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{ahindle@uwaterloo.ca}
\alignauthor  Neil A. Ernst\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{nernst@cs.toronto.edu}
\and
\alignauthor Michael W. Godfrey\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{migod@uwaterloo.ca}
\alignauthor Richard C. Holt \\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{holt@uwaterloo.ca}
\alignauthor John Mylopoulos \\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{jm@cs.toronto.edu}
}

@@

\begin{abstract}
\todo[inline]{Topics and LDA sooner, Topics/concept location is a known
  research area and we're saying they don't do enough}

  Within the field of mining software repositories, many approaches,   such as topic modeling and concept location, rely on the automated   application of machine learning algorithms to corpora.  
 Unfortunately the output of these tools is often difficult to distinguish and interpret as they are often so abstract.
 Thus to have a meaningful discussion about the topics of software development, we must be able to devise appropriate labels for extracted topics. 
 However, these approaches neither use domain-specific knowledge to improve results, nor contextualize those results for developers.   While too much specificity can produce non-generalizable results, too little produces broad learners that do not provide much immediately useful detail. 
 This paper implements \emph{labelled topic extraction}, in which topics are extracted from commit comments and given labels relating to a cross-project taxonomy. We focus on non-functional requirements related to software quality as a potential generalization, since there is some shared belief that these qualities apply broadly across many software systems and their development artifacts.  
 We evaluated our approach with an experimental study on two large-scale database projects, MySQL and MaxDB. We extracted topics using Latent Dirichlet Allocation (LDA) from the commit log comments of their version control systems (CVS and BitKeeper). Our results were generalizable across the two projects, showing that non-functional requirements were commonly discussed, and we identified topic trends over time. 	
 Our labelled topic extraction technique allowed us to devise appropriate, context-sensitive labels across these two projects, providing insight into software development activities.
\end{abstract}

>>>>

\begin{document}

\conferenceinfo{ICSE}{'11 Waikiki, Hawaii USA}
\numberofauthors{5}
\author{
\alignauthor 
Abram Hindle\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{ahindle@uwaterloo.ca}
\alignauthor  Neil A. Ernst\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{nernst@cs.toronto.edu}
\and
\alignauthor Michael W. Godfrey\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{migod@uwaterloo.ca}
\alignauthor Richard C. Holt \\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{holt@uwaterloo.ca}
\alignauthor John Mylopoulos \\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{jm@cs.toronto.edu}
}

@@

\begin{abstract}
%\todo[inline]{Topics and LDA sooner, Topics/concept location is a known
%  research area and we're saying they don't do enough}

% our field
  Within the field of mining software repositories, many approaches,   such as topic modeling and concept location, rely on the automated   application of machine learning algorithms to corpora.  
% the problem
 Unfortunately the output of these tools is often difficult to distinguish and interpret as they are often so abstract, in particular topics that are automatically extracted are word-lists lacking semantic interpretation.
% the solution 
 Thus to have a meaningful discussion about the topics of software development, we must be able to interpret these topics and devise appropriate labels for extracted topics, yet current software engineering topic analysis and concept analysis research relies on manual naming and labelling of topics
% the labelling research
Current topic labelling approaches neither use domain-specific knowledge to improve results, nor contextualize those results for developers.   
% a sub problem
While too much specificity can produce non-generalizable results, too little produces broad learners that do not provide much immediately useful detail. 
% what we do
This paper implements \emph{labelled topic extraction}, in which topics are extracted from commit comments and given labels relating to a cross-project taxonomy. 
% data mining generalizable
To ensure we have a generalizable project agnostic approach we label topics by non-functional requirements related to software quality, since there is some shared belief that these qualities apply broadly across many software systems and their development artifacts.
% We used real world data
We evaluated our approach with an experimental study on two large-scale database projects, MySQL and MaxDB. 
% We used LDA, CVS, Bitkeeper
We extracted topics using Latent Dirichlet Allocation (LDA) from the commit log comments of their version control systems (CVS and BitKeeper). 
% We show NFRs exist
Our results were generalizable across the two projects, showing that non-functional requirements were commonly discussed, and we identified topic trends over time. 	
% we can label stuff
Our labelled topic extraction technique allowed us to devise appropriate, context-sensitive labels across these two projects, providing insight into their software development activities.
\end{abstract}

\category{D.2.9}{Software Engineering}{Managment}[Lifecycle]
\category{D.2.1}{Software Engineering}{Requirements/Specifications}[Tools]

%\terms{Theory}

\keywords{Topics, LDA, NFR}
